The Astropy Project: Building an open-science project and status of the v2.0 core package

### 2018-03-13 response.txt

We thank the referee for the close reading of the paper and the insightful
comments.  We provide a response to specific comments from the referee
and the statistical editor below.

> There are some stylistic issues with the text. I have left comments inline
>  where appropriate.

We have addressed all of the stylistic issues that were raised by the referee.
Here are some responses to the more detailed comments:

Comment on health of the project:

We have added a plot of contributors per month along with our other metrics
and some further comments about the health of the project.  A full analysis
following the CHAOSS framework is beyond the scope of the current paper.

@@

> More generally, given the technical nature of the work being described here,
> I frequently found myself wanting a small code snippet that demonstrated the
> new/improved functionality of the packages being described. Perhaps the
> authors could find a way to include short code examples where appropriate,
> either inline in the paper body or in the appendix.

We did include code snippets in the first astropy paper from 2013. 
However, we have made a conscious decision to avoid that this time 
due to the following reasons:

- While we aim for stability, many of the newsest features are still
  considered provisional, meaning that their API can still change. The
  paper describes astropy 2.0, but at the time of writing this,
  astropy 3.0 is already released. We hope that this paper is useful
  for years to come. Code examples for a specific version are at risk
  of being outdated much sooner than that.

- Code examples belong in the documentation. In the documentation at
  docs.astropy.org we provide extensive examples with enough comments
  to actually understand what is going on. If readers are curious, we
  want them to read the documentation.

### 2018-03-14 registry.tex

\href{http://github.com/aplpy/aplpy.git}{APLpy} & Yes & \href{https://pypi.python.org/pypi/APLpy}{APLpy} & Thomas Robitaille and Eli Bressert &  \\

@@

\href{http://github.com/astroML/astroML}{astroML} & Yes & \href{https://pypi.python.org/pypi/astroML}{astroML} & Jake Vanderplas &  \\

@@

\href{http://github.com/astropy/astroquery.git}{astroquery} & Yes & \href{https://pypi.python.org/pypi/astroquery}{astroquery} & Adam Ginsburg and Brigitta Sipocz & \citealt{astroquery} \\
\href{http://github.com/astropy/ccdproc.git}{ccdproc} & Yes & \href{https://pypi.python.org/pypi/ccdproc}{ccdproc} & Steven Crawford, Matt Craig, and Michael Seifert & \citealt{ccdproc} \\

@@

\href{http://github.com/gammapy/gammapy.git}{gammapy} & No & \href{https://pypi.python.org/pypi/gammapy}{gammapy} & Christoph Deil & \citealt{gammapy} \\
\href{http://github.com/ejeschke/ginga}{ginga} & Yes & \href{https://pypi.python.org/pypi/ginga}{ginga} & Eric Jeschke and Pey-Lian Lim & \citealt{ginga} \\
\href{https://github.com/glue-viz/glue.git}{Glue} & Yes & \href{https://pypi.python.org/pypi/glueviz}{glueviz} & Chris Beaumont and Thomas Robitaille & \citealt{glue} \\
\href{https://github.com/spacetelescope/gwcs.git}{gwcs} & No & \href{https://pypi.python.org/pypi/gwcs}{gwcs} & Nadia Dencheva & \citealt{gwcs} \\

@@

\href{https://github.com/StingraySoftware/HENDRICS}{HENDRICS} & Yes & \href{https://pypi.python.org/pypi/hendrics}{hendrics} & Matteo Bachetti &  \\
\href{https://github.com/hipspy/hips}{hips} & No & \href{https://pypi.python.org/pypi/hips}{hips} & Christoph Deil and Thomas Boch &  \\
\href{http://github.com/spacetelescope/imexam}{imexam} & No & \href{https://pypi.python.org/pypi/imexam}{imexam} & Megan Sosey & \citealt{imexam} \\
\href{https://github.com/linetools/linetools}{linetools} & Yes & \href{https://pypi.python.org/pypi/linetools}{linetools} & J. Xavier Prochaska, Nicolas Tejos, and Neil Crighton &  \\

@@

\href{https://github.com/RiceMunk/omnifit}{omnifit} & Yes & \href{https://pypi.python.org/pypi/omnifit}{omnifit} & Aleksi Suutarinen &  \\
\href{http://github.com/astropy/photutils.git}{photutils} & No & \href{https://pypi.python.org/pypi/photutils}{photutils} & Larry Bradley and Brigitta Sipocz & \citealt{photutils} \\

@@

\href{http://github.com/weaverba137/pydl.git}{PyDL} & No & \href{https://pypi.python.org/pypi/pydl}{pydl} & Benjamin Alan Weaver & \citealt{pydl} \\
\href{https://github.com/astropy/pyregion.git}{pyregion} & Yes & \href{https://pypi.python.org/pypi/pyregion}{pyregion} & Jae-Joon Lee and Christoph Deil &  \\

@@

\href{https://github.com/pyvirtobs/pyvo.git}{PyVO} & No & \href{https://pypi.python.org/pypi/pyvo}{pyvo} & Stefan Becker &  \\
\href{https://github.com/astropy/regions}{regions} & No & \href{https://pypi.python.org/pypi/regions}{regions} & Christoph Deil and Johannes King &  \\
\href{https://github.com/astrofrog/reproject.git}{reproject} & Yes & \href{https://pypi.python.org/pypi/reproject}{reproject} & Thomas Robitaille &  \\
\href{http://github.com/sncosmo/sncosmo}{sncosmo} & Yes & \href{https://pypi.python.org/pypi/sncosmo}{sncosmo} & Kyle Barbary & \citealt{sncosmo} \\

@@

\href{http://github.com/astropy/specutils.git}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & Nicholas Earl, Adam Ginsburg, Steve Crawford, Erik Tollerud &  \\
\href{https://github.com/spacetelescope/spherical_geometry.git}{spherical\_geometry} & No & \href{https://pypi.python.org/pypi/spherical-geometry}{spherical-geometry} & Bernie Simon and Michael Droettboom &  \\
\href{https://github.com/StingraySoftware/stingray}{stingray} & No & \href{https://pypi.python.org/pypi/stingray}{stingray} & Daniela Huppenkothen, Matteo Bachetti, Abigail Stevens, Simone Migliari, and Paul Balm &  \\

>>>>

\href{https://github.com/aplpy/aplpy}{APLpy} & Yes & \href{https://pypi.python.org/pypi/APLpy}{APLpy} & Thomas Robitaille and Eli Bressert & \citealt{aplpy} \\

@@

\href{https://github.com/astroML/astroML}{astroML} & Yes & \href{https://pypi.python.org/pypi/astroML}{astroML} & Jake Vanderplas & \citealt{astroML_conf, astroML_book} \\

@@

\href{https://github.com/astropy/astroquery}{astroquery} & Yes & \href{https://pypi.python.org/pypi/astroquery}{astroquery} & Adam Ginsburg and Brigitta Sipocz & \citealt{astroquery} \\
\href{https://github.com/astropy/ccdproc}{ccdproc} & Yes & \href{https://pypi.python.org/pypi/ccdproc}{ccdproc} & Steven Crawford, Matt Craig, and Michael Seifert & \citealt{ccdproc} \\

@@

\href{https://github.com/gammapy/gammapy}{gammapy} & No & \href{https://pypi.python.org/pypi/gammapy}{gammapy} & Christoph Deil & \citealt{gammapy} \\
\href{https://github.com/ejeschke/ginga}{ginga} & Yes & \href{https://pypi.python.org/pypi/ginga}{ginga} & Eric Jeschke and Pey-Lian Lim & \citealt{ginga} \\
\href{https://github.com/glue-viz/glue}{Glue} & Yes & \href{https://pypi.python.org/pypi/glueviz}{glueviz} & Chris Beaumont and Thomas Robitaille & \citealt{glue} \\
\href{https://github.com/spacetelescope/gwcs}{gwcs} & No & \href{https://pypi.python.org/pypi/gwcs}{gwcs} & Nadia Dencheva & \citealt{gwcs} \\

@@

\href{https://github.com/StingraySoftware/HENDRICS}{HENDRICS} & Yes & \href{https://pypi.python.org/pypi/hendrics}{hendrics} & Matteo Bachetti & \citealt{hendrics} \\
\href{https://github.com/hipspy/hips}{hips} & No & \href{https://pypi.python.org/pypi/hips}{hips} & Christoph Deil and Thomas Boch & \citealt{hips} \\
\href{https://github.com/spacetelescope/imexam}{imexam} & No & \href{https://pypi.python.org/pypi/imexam}{imexam} & Megan Sosey & \citealt{imexam} \\
\href{https://github.com/linetools/linetools}{linetools} & Yes & \href{https://pypi.python.org/pypi/linetools}{linetools} & J. Xavier Prochaska, Nicolas Tejos, and Neil Crighton & \citealt{linetools} \\

@@

\href{https://github.com/RiceMunk/omnifit}{omnifit} & Yes & \href{https://pypi.python.org/pypi/omnifit}{omnifit} & Aleksi Suutarinen & \citealt{omnifit} \\
\href{https://github.com/astropy/photutils}{photutils} & No & \href{https://pypi.python.org/pypi/photutils}{photutils} & Larry Bradley and Brigitta Sipocz & \citealt{photutils} \\

@@

\href{https://github.com/weaverba137/pydl}{PyDL} & No & \href{https://pypi.python.org/pypi/pydl}{pydl} & Benjamin Alan Weaver & \citealt{pydl} \\
\href{https://github.com/astropy/pyregion}{pyregion} & Yes & \href{https://pypi.python.org/pypi/pyregion}{pyregion} & Jae-Joon Lee and Christoph Deil & \citealt{pyregions} \\

@@

\href{https://github.com/pyvirtobs/pyvo}{PyVO} & No & \href{https://pypi.python.org/pypi/pyvo}{pyvo} & Stefan Becker & \citealt{pyvo} \\
\href{https://github.com/astropy/regions}{regions} & No & \href{https://pypi.python.org/pypi/regions}{regions} & Christoph Deil and Johannes King & \citealt{regions} \\
\href{https://github.com/astrofrog/reproject}{reproject} & Yes & \href{https://pypi.python.org/pypi/reproject}{reproject} & Thomas Robitaille & \citealt{reproject} \\
\href{https://github.com/sncosmo/sncosmo}{sncosmo} & Yes & \href{https://pypi.python.org/pypi/sncosmo}{sncosmo} & Kyle Barbary & \citealt{sncosmo} \\

@@

\href{https://github.com/astropy/specutils}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & Nicholas Earl, Adam Ginsburg, Steve Crawford, and Erik Tollerud & \citealt{specutils} \\
\href{https://github.com/spacetelescope/spherical_geometry}{spherical\_geometry} & No & \href{https://pypi.python.org/pypi/spherical-geometry}{spherical-geometry} & Bernie Simon &  \\
\href{https://github.com/StingraySoftware/stingray}{stingray} & No & \href{https://pypi.python.org/pypi/stingray}{stingray} & Daniela Huppenkothen, Matteo Bachetti, Abigail Stevens, Simone Migliari, and Paul Balm & \citealt{stingray} \\
\href{https://github.com/spacetelescope/synphot_refactor}{synphot} & Yes & \href{https://pypi.python.org/pypi/synphot}{synphot} & Pey Lian Lim & \citealt{synphot} \\
